%------------------------
% Resume Template
% Author : Parin Kasabia
% Github : https://github.com/mateurdreaming
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

% Import packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

% Page layout
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Parin Kasabia}} & Email:~~ \href{mailto:mailto:pkasabia0909@gmail.com}{pkasabia0909@gmail.com}\\
  \href{https://linkedin.com/in/parinkasabia}{LinkedIn: linkedin.com/in/parinkasabia} & Mobile:~~~~~~~~~~~~ +XX-XXX-XXX-XXX \\
  \href{https://github.com/MateUrDreaming}{Github: \,\, github.com/MateUrDreaming} & Location: Auckland, New Zealand \\
\end{tabular*}

%-----------OBJECTIVE-----------------
\section{Objective}
{Passionate entry level data engineer with a foundational understanding of data pipelines, data processing, and cloud platforms. Familiar with SQL, Python, and ETL basics, with a strong commitment to continuous learning and skill development. Eager to support data-driven teams by ensuring data accuracy, optimizing data flow,and build technical skills by contributing to impactful projects.}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Auckland}{Auckland, New Zealand}
      {Bachelors of Commerce and Science - Computer Science \& Information systems; GPA: A-}{2021 - 2025}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:}  Artificial Intelligence, Cloud Computing, Databases, IT infrastructure, Machine Learning, Networking,  Solutions Architecture}}}

    \resumeSubheading
      {Orewa College}{Auckland, New Zealand}
      {Level 3 Certificate (University Enterence); Excellence endorsement A+ }{2014 - 2020}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Digital Technologies, Maths, Statistics, Physics, English, History}}}
    \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\vspace{-7pt}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, SQL, Javascript, Bash, Java}
	\resumeSubItem{Frameworks}{~~~~Scikit, NLTK, TensorFlow, Keras, Django, Flask, NodeJS}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Office 365, Docker, GIT, PostgreSQL, MySQL, SQLite}
	\resumeSubItem{Platforms}{~~~~~~~Linux, Web, Windows, MacOS, Raspberry, AWS, Azure}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Provident Insurance}{Auckland, New Zealand (Remote)}
    {Administrative Assistant (Full-time)}{November 2021 - March 2022}
        \resumeItemListStart
              \resumeItem{Customer Service}
              {Used various communication channels to assist customers with queries about their current policy.}
              \resumeItem{Fetching Data}
              {Wrote SQL queries in PICLOS to access customer policies need to be amended to renewed.}
              \resumeItem{Processing Payments}{Handled debit control for policy renewals on weekly, fortnightly and monthly payments using Debit success and Windcave. I would also use Xero to process a policy that has been paid in full.}
              \resumeItem{Guides and Training}{Developed guides on how to bind policies,  and offer policy renewals on the PICLOS system for upcoming staff. I also trained colleagues on using the system efficiently to complete renewals. }
              \resumeItem{Excel Calculators}{Developed excel calculators to efficiently gauge payment history and determine amount during policy renewals using CSV's offered by Debit success and Windcave. }
          \resumeItemListEnd
    \resumeSubheading{Pizza Jacks Silverdale}{Auckland, New Zealand (On-site)}
    {Jacks Crew (Full-time)}{November 2020 - August 2021}
        \resumeItemListStart
               \resumeItem{Customer Service}
              {Provided friendly and efficient service, handling customer orders both in-store and via phone, addressing inquiries, and resolving issues to ensure a positive customer experience.}
              \resumeItem{Team Collaboration}
              {Worked closely with team members in a fast-paced environment, assisting in food preparation, managing inventory, and ensuring timely delivery of orders.}
              \resumeItem{Cash Handling}
              {Managed cash transactions accurately and efficiently, balancing the cash register and following protocols for secure financial handling.}
              \resumeItem{Store Management}
              {Assumed store management duties as needed, supervising team operations, coordinating staff tasks, and ensuring smooth service during peak hours.}
          \resumeItemListEnd
        \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Signature Sounds - Web music repository}{ A simple web application developed with Flask, designed as a music repository where users can upload, categorize, and search for music files. The application features user authentication, personalized playlists, and a search function for exploring sounds by genre, artist, or tag. \\Tech: Python, SQLAlchemy, Flask, Jinja, Bootstrap5, Github (October 2022)}
\vspace{2pt}
\resumeSubItem{PDFMadeEZ - PDF Extraction tool}{A PDF-to-HTML conversion tool built to streamline text extraction while preserving original formatting. Using PyMuPDF, we can extract elements from the PDF with 98\% accuracy and use RegEx to properly format text for easier use in notes. This tool improved efficiency in processing lecture slides by 30\%.\\
Tech: Python, PyMuPDF, RegEx, HTML. (September 2023)}

\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------VOLUNTEER EXPERIENCE-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Class Representative at University of Auckland}{Auckland, New Zealand}
    {Communicated student feedback for INFOSYS 110, INFOSYS 220 and COMPSCI 361.}
    { 2021 - Present}
    \resumeSubheading
    {WWDC X SEAS Hackathon [Rewriting History] }{Auckland, New Zealand}
    {Developed a prompted historical image generator using Dall-E in a team of 6 using NextJS.  }{July 2023}

\resumeSubHeadingListEnd

\end{document}